---
title: "Tutorial for Simulation study in the unconditional case in the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability in a Three-Class Disease Setting\" " 
author: "Zhaoxi Zhang, Vanda Inácio, and Miguel de Carvalho"
output: github_document
#bibliography: reference.bib
#csl: modern-language-association.csl
---

In this tutorial we describe the steps for obtaining the results of the simulation study in the unconditional case in Section 5.1 of the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability in a Three-Class Disease Setting\".

As a preliminary step, we load on a clean environment all the required libraries.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As a preliminary step, we load on a clean environment all the required libraries.
```{r, eval=FALSE}
library(LSBP)    # Load the LSBP package
library(ggplot2) # Graphical library
library(coda)    # For MCMC analysis
library(splines) # For computing the natural B-splines basis
library(pracma)
library(DIRECT)
library(sn)
library(nor1mix)
library(future)
library(future.apply)
library(rjags)
```

We need to load some predefined functions the simulation study in the unconditional case. 
```{r, include=FALSE}
source("../functions/unconditional_simulation_functions.R")
```

```{r, eval=FALSE}
source("../functions/unconditional_simulation_functions.R")
```

Because we conduct the estimation of underlap repeatedly for 100 datasets in each scenario, so the process could be accelerated by parallelizing the computation. Here I use the future package to demonstrate one way of parallelizing the code, the utilization of the future package is incorporated in the simulation_unl_uncon function.