---
title: "Tutorial for Simulation study in the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability in a Three-Class Disease Setting\" " 
author: "Zhaoxi Zhang, Vanda Inácio, and Miguel de Carvalho"
output: github_document
#bibliography: reference.bib
#csl: modern-language-association.csl
---

In this tutorial we describe the steps for obtaining the results of the Simulation study in Section 4 of the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability in a Three-Class Disease Setting\".

As a preliminary step, we load on a clean environment all the required libraries.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The code described below requires the installation of the UNL.est package, available in this repository. See the README for instructions on the installation.

```{r, include=FALSE}
load(file="D:/PhD_study2_desktop/functions/results/cluster_tutorial_results.RData")
library(ggplot2)
```

As a preliminary step, we load on a clean environment all the required libraries.
```{r, eval=FALSE}
library(LSBP)    # Load the LSBP package
library(ggplot2) # Graphical library
library(coda)    # For MCMC analysis
library(splines) # For computing the natural B-splines basis
library(pracma)
library(DIRECT)
library(sn)
library(nor1mix)
library(future)
library(future.apply)
library(rjags)
```

Also, for illustration purpose, we load some functions for clustering based on the linear dependent Dirichlet process (LDDP) mixture models which are not the focus of the UNL.est package. 
```{r, eval=FALSE}
source("functions/unconditional_simulation_functions.R")
```

```{r, eval=FALSE}
getwd()
```

