---
title: "Tutorial for Simulation study in the unconditional case in the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability\" " 
author: "Zhaoxi Zhang, Vanda Inácio, and Miguel de Carvalho"
output: github_document
#bibliography: reference.bib
#csl: modern-language-association.csl
---

In this tutorial we describe the steps for obtaining the results of the simulation study in the unconditional case in Section 4.1 of the paper \"The Underlap Coefficient as Measure of a Biomarker’s Discriminatory Ability\".

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As a preliminary step, we load on a clean environment all the required libraries.
```{r, eval=FALSE}
library(sn)
library(nor1mix)
library(future)
library(future.apply)
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE}
library(sn)
library(nor1mix)
library(future)
library(future.apply)
library(ggplot2)
library(dplyr)
```

We need to load some predefined functions for the simulation study in the unconditional case. 
```{r, include=FALSE}
source("../functions/unconditional_simulation_functions.R")
```

```{r, eval=FALSE}
source("../functions/unconditional_simulation_functions.R")
```

Because we conduct the estimation of underlap repeatedly for 100 datasets in each scenario for both the DPM estimator and the DPM-BB estimator, so the process could be accelerated by parallelizing the computation. Here I use the future package to demonstrate one way of parallelizing the code, the utilization of the future package is incorporated in the simulation_unl_uncon function.
```{r, eval=FALSE}
plan(multisession, workers = parallel::detectCores()-2)
nrep=100;nsave=5000;nburn=2000
nlist1=list(n1=100,n2=100,n3=100)
nlist2=list(n1=200,n2=200,n3=200)
nlist3=list(n1=500,n2=500,n3=500)
nlist4=list(n1=1000,n2=1000,n3=1000)
nlist5=list(n1=100,n2=300,n3=500)
##case1 simulation
simu_unconc1_s1=simulation_unl_uncon(case=1,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc1_s2=simulation_unl_uncon(case=1,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc1_s3=simulation_unl_uncon(case=1,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc1_s4=simulation_unl_uncon(case=1,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc1_s5=simulation_unl_uncon(case=1,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case2 simulation
simu_unconc2_s1=simulation_unl_uncon(case=2,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc2_s2=simulation_unl_uncon(case=2,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc2_s3=simulation_unl_uncon(case=2,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc2_s4=simulation_unl_uncon(case=2,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc2_s5=simulation_unl_uncon(case=2,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case3 simulation
simu_unconc3_s1=simulation_unl_uncon(case=3,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc3_s2=simulation_unl_uncon(case=3,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc3_s3=simulation_unl_uncon(case=3,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc3_s4=simulation_unl_uncon(case=3,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc3_s5=simulation_unl_uncon(case=3,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case4 simulation
simu_unconc4_s1=simulation_unl_uncon(case=4,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc4_s2=simulation_unl_uncon(case=4,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc4_s3=simulation_unl_uncon(case=4,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc4_s4=simulation_unl_uncon(case=4,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc4_s5=simulation_unl_uncon(case=4,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case5 simulation
simu_unconc5_s1=simulation_unl_uncon(case=5,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc5_s2=simulation_unl_uncon(case=5,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc5_s3=simulation_unl_uncon(case=5,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc5_s4=simulation_unl_uncon(case=5,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc5_s5=simulation_unl_uncon(case=5,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case6 simulation
simu_unconc6_s1=simulation_unl_uncon(case=6,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc6_s2=simulation_unl_uncon(case=6,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc6_s3=simulation_unl_uncon(case=6,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc6_s4=simulation_unl_uncon(case=6,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc6_s5=simulation_unl_uncon(case=6,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case7 simulation
simu_unconc7_s1=simulation_unl_uncon(case=7,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc7_s2=simulation_unl_uncon(case=7,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc7_s3=simulation_unl_uncon(case=7,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc7_s4=simulation_unl_uncon(case=7,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc7_s5=simulation_unl_uncon(case=7,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case8 simulation
simu_unconc8_s1=simulation_unl_uncon(case=8,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc8_s2=simulation_unl_uncon(case=8,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc8_s3=simulation_unl_uncon(case=8,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc8_s4=simulation_unl_uncon(case=8,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc8_s5=simulation_unl_uncon(case=8,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case9 simulation
simu_unconc9_s1=simulation_unl_uncon(case=9,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc9_s2=simulation_unl_uncon(case=9,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc9_s3=simulation_unl_uncon(case=9,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc9_s4=simulation_unl_uncon(case=9,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
simu_unconc9_s5=simulation_unl_uncon(case=9,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)

##case1 simulation
bb_simu_unconc1_s1=simulation_unl_uncon_bb(case=1,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc1_s2=simulation_unl_uncon_bb(case=1,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc1_s3=simulation_unl_uncon_bb(case=1,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc1_s4=simulation_unl_uncon_bb(case=1,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc1_s5=simulation_unl_uncon_bb(case=1,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case2 simulation
bb_simu_unconc2_s1=simulation_unl_uncon_bb(case=2,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc2_s2=simulation_unl_uncon_bb(case=2,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc2_s3=simulation_unl_uncon_bb(case=2,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc2_s4=simulation_unl_uncon_bb(case=2,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc2_s5=simulation_unl_uncon_bb(case=2,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case3 simulation
bb_simu_unconc3_s1=simulation_unl_uncon_bb(case=3,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc3_s2=simulation_unl_uncon_bb(case=3,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc3_s3=simulation_unl_uncon_bb(case=3,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc3_s4=simulation_unl_uncon_bb(case=3,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc3_s5=simulation_unl_uncon_bb(case=3,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case4 simulation
bb_simu_unconc4_s1=simulation_unl_uncon_bb(case=4,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc4_s2=simulation_unl_uncon_bb(case=4,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc4_s3=simulation_unl_uncon_bb(case=4,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc4_s4=simulation_unl_uncon_bb(case=4,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc4_s5=simulation_unl_uncon_bb(case=4,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case5 simulation
bb_simu_unconc5_s1=simulation_unl_uncon_bb(case=5,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc5_s2=simulation_unl_uncon_bb(case=5,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc5_s3=simulation_unl_uncon_bb(case=5,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc5_s4=simulation_unl_uncon_bb(case=5,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc5_s5=simulation_unl_uncon_bb(case=5,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case6 simulation
bb_simu_unconc6_s1=simulation_unl_uncon_bb(case=6,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc6_s2=simulation_unl_uncon_bb(case=6,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc6_s3=simulation_unl_uncon_bb(case=6,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc6_s4=simulation_unl_uncon_bb(case=6,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc6_s5=simulation_unl_uncon_bb(case=6,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case7 simulation
bb_simu_unconc7_s1=simulation_unl_uncon_bb(case=7,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc7_s2=simulation_unl_uncon_bb(case=7,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc7_s3=simulation_unl_uncon_bb(case=7,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc7_s4=simulation_unl_uncon_bb(case=7,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc7_s5=simulation_unl_uncon_bb(case=7,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case8 simulation
bb_simu_unconc8_s1=simulation_unl_uncon_bb(case=8,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc8_s2=simulation_unl_uncon_bb(case=8,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc8_s3=simulation_unl_uncon_bb(case=8,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc8_s4=simulation_unl_uncon_bb(case=8,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc8_s5=simulation_unl_uncon_bb(case=8,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
##case9 simulation
bb_simu_unconc9_s1=simulation_unl_uncon_bb(case=9,nlist=nlist1,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc9_s2=simulation_unl_uncon_bb(case=9,nlist=nlist2,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc9_s3=simulation_unl_uncon_bb(case=9,nlist=nlist3,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc9_s4=simulation_unl_uncon_bb(case=9,nlist=nlist4,nrep=nrep,nsave=nsave,nburn=nburn)
bb_simu_unconc9_s5=simulation_unl_uncon_bb(case=9,nlist=nlist5,nrep=nrep,nsave=nsave,nburn=nburn)
```

```{r, include=FALSE}
load("//csce.datastore.ed.ac.uk/csce/maths/groups/mdt/simulation_data/revision_bio/simu_uncon_dpm_bb.RData")
load("//csce.datastore.ed.ac.uk/csce/maths/groups/mdt/simulation_data/revision_bio/simu_uncon_dpm.RData")

nrep=100;nsave=5000;nburn=2000
nlist1=list(n1=100,n2=100,n3=100)
nlist2=list(n1=200,n2=200,n3=200)
nlist3=list(n1=500,n2=500,n3=500)
nlist4=list(n1=1000,n2=1000,n3=1000)
nlist5=list(n1=100,n2=300,n3=500)
```

We need to use the function tranform_list_simu to transform the results from future_lapply to a more interpretable manner.
```{r}
simu_unconc1_s1=tranform_list_simu(simu_unconc1_s1,nsave=nsave,nrep = nrep)
simu_unconc1_s2=tranform_list_simu(simu_unconc1_s2,nsave=nsave,nrep = nrep)
simu_unconc1_s3=tranform_list_simu(simu_unconc1_s3,nsave=nsave,nrep = nrep)
simu_unconc1_s4=tranform_list_simu(simu_unconc1_s4,nsave=nsave,nrep = nrep)
simu_unconc1_s5=tranform_list_simu(simu_unconc1_s5,nsave=nsave,nrep = nrep)

simu_unconc2_s1=tranform_list_simu(simu_unconc2_s1,nsave=nsave,nrep = nrep)
simu_unconc2_s2=tranform_list_simu(simu_unconc2_s2,nsave=nsave,nrep = nrep)
simu_unconc2_s3=tranform_list_simu(simu_unconc2_s3,nsave=nsave,nrep = nrep)
simu_unconc2_s4=tranform_list_simu(simu_unconc2_s4,nsave=nsave,nrep = nrep)
simu_unconc2_s5=tranform_list_simu(simu_unconc2_s5,nsave=nsave,nrep = nrep)

simu_unconc3_s1=tranform_list_simu(simu_unconc3_s1,nsave=nsave,nrep = nrep)
simu_unconc3_s2=tranform_list_simu(simu_unconc3_s2,nsave=nsave,nrep = nrep)
simu_unconc3_s3=tranform_list_simu(simu_unconc3_s3,nsave=nsave,nrep = nrep)
simu_unconc3_s4=tranform_list_simu(simu_unconc3_s4,nsave=nsave,nrep = nrep)
simu_unconc3_s5=tranform_list_simu(simu_unconc3_s5,nsave=nsave,nrep = nrep)

simu_unconc4_s1=tranform_list_simu(simu_unconc4_s1,nsave=nsave,nrep = nrep)
simu_unconc4_s2=tranform_list_simu(simu_unconc4_s2,nsave=nsave,nrep = nrep)
simu_unconc4_s3=tranform_list_simu(simu_unconc4_s3,nsave=nsave,nrep = nrep)
simu_unconc4_s4=tranform_list_simu(simu_unconc4_s4,nsave=nsave,nrep = nrep)
simu_unconc4_s5=tranform_list_simu(simu_unconc4_s5,nsave=nsave,nrep = nrep)

simu_unconc5_s1=tranform_list_simu(simu_unconc5_s1,nsave=nsave,nrep = nrep)
simu_unconc5_s2=tranform_list_simu(simu_unconc5_s2,nsave=nsave,nrep = nrep)
simu_unconc5_s3=tranform_list_simu(simu_unconc5_s3,nsave=nsave,nrep = nrep)
simu_unconc5_s4=tranform_list_simu(simu_unconc5_s4,nsave=nsave,nrep = nrep)
simu_unconc5_s5=tranform_list_simu(simu_unconc5_s5,nsave=nsave,nrep = nrep)

simu_unconc6_s1=tranform_list_simu(simu_unconc6_s1,nsave=nsave,nrep = nrep)
simu_unconc6_s2=tranform_list_simu(simu_unconc6_s2,nsave=nsave,nrep = nrep)
simu_unconc6_s3=tranform_list_simu(simu_unconc6_s3,nsave=nsave,nrep = nrep)
simu_unconc6_s4=tranform_list_simu(simu_unconc6_s4,nsave=nsave,nrep = nrep)
simu_unconc6_s5=tranform_list_simu(simu_unconc6_s5,nsave=nsave,nrep = nrep)

simu_unconc7_s1=tranform_list_simu(simu_unconc7_s1,nsave=nsave,nrep = nrep)
simu_unconc7_s2=tranform_list_simu(simu_unconc7_s2,nsave=nsave,nrep = nrep)
simu_unconc7_s3=tranform_list_simu(simu_unconc7_s3,nsave=nsave,nrep = nrep)
simu_unconc7_s4=tranform_list_simu(simu_unconc7_s4,nsave=nsave,nrep = nrep)
simu_unconc7_s5=tranform_list_simu(simu_unconc7_s5,nsave=nsave,nrep = nrep)

simu_unconc8_s1=tranform_list_simu(simu_unconc8_s1,nsave=nsave,nrep = nrep)
simu_unconc8_s2=tranform_list_simu(simu_unconc8_s2,nsave=nsave,nrep = nrep)
simu_unconc8_s3=tranform_list_simu(simu_unconc8_s3,nsave=nsave,nrep = nrep)
simu_unconc8_s4=tranform_list_simu(simu_unconc8_s4,nsave=nsave,nrep = nrep)
simu_unconc8_s5=tranform_list_simu(simu_unconc8_s5,nsave=nsave,nrep = nrep)

simu_unconc9_s1=tranform_list_simu(simu_unconc9_s1,nsave=nsave,nrep = nrep)
simu_unconc9_s2=tranform_list_simu(simu_unconc9_s2,nsave=nsave,nrep = nrep)
simu_unconc9_s3=tranform_list_simu(simu_unconc9_s3,nsave=nsave,nrep = nrep)
simu_unconc9_s4=tranform_list_simu(simu_unconc9_s4,nsave=nsave,nrep = nrep)
simu_unconc9_s5=tranform_list_simu(simu_unconc9_s5,nsave=nsave,nrep = nrep)
##bb
bb_simu_unconc1_s1=tranform_list_simu(bb_simu_unconc1_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc1_s2=tranform_list_simu(bb_simu_unconc1_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc1_s3=tranform_list_simu(bb_simu_unconc1_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc1_s4=tranform_list_simu(bb_simu_unconc1_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc1_s5=tranform_list_simu(bb_simu_unconc1_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc2_s1=tranform_list_simu(bb_simu_unconc2_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc2_s2=tranform_list_simu(bb_simu_unconc2_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc2_s3=tranform_list_simu(bb_simu_unconc2_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc2_s4=tranform_list_simu(bb_simu_unconc2_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc2_s5=tranform_list_simu(bb_simu_unconc2_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc3_s1=tranform_list_simu(bb_simu_unconc3_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc3_s2=tranform_list_simu(bb_simu_unconc3_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc3_s3=tranform_list_simu(bb_simu_unconc3_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc3_s4=tranform_list_simu(bb_simu_unconc3_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc3_s5=tranform_list_simu(bb_simu_unconc3_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc4_s1=tranform_list_simu(bb_simu_unconc4_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc4_s2=tranform_list_simu(bb_simu_unconc4_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc4_s3=tranform_list_simu(bb_simu_unconc4_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc4_s4=tranform_list_simu(bb_simu_unconc4_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc4_s5=tranform_list_simu(bb_simu_unconc4_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc5_s1=tranform_list_simu(bb_simu_unconc5_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc5_s2=tranform_list_simu(bb_simu_unconc5_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc5_s3=tranform_list_simu(bb_simu_unconc5_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc5_s4=tranform_list_simu(bb_simu_unconc5_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc5_s5=tranform_list_simu(bb_simu_unconc5_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc6_s1=tranform_list_simu(bb_simu_unconc6_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc6_s2=tranform_list_simu(bb_simu_unconc6_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc6_s3=tranform_list_simu(bb_simu_unconc6_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc6_s4=tranform_list_simu(bb_simu_unconc6_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc6_s5=tranform_list_simu(bb_simu_unconc6_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc7_s1=tranform_list_simu(bb_simu_unconc7_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc7_s2=tranform_list_simu(bb_simu_unconc7_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc7_s3=tranform_list_simu(bb_simu_unconc7_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc7_s4=tranform_list_simu(bb_simu_unconc7_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc7_s5=tranform_list_simu(bb_simu_unconc7_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc8_s1=tranform_list_simu(bb_simu_unconc8_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc8_s2=tranform_list_simu(bb_simu_unconc8_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc8_s3=tranform_list_simu(bb_simu_unconc8_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc8_s4=tranform_list_simu(bb_simu_unconc8_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc8_s5=tranform_list_simu(bb_simu_unconc8_s5,nsave=nsave,nrep = nrep)

bb_simu_unconc9_s1=tranform_list_simu(bb_simu_unconc9_s1,nsave=nsave,nrep = nrep)
bb_simu_unconc9_s2=tranform_list_simu(bb_simu_unconc9_s2,nsave=nsave,nrep = nrep)
bb_simu_unconc9_s3=tranform_list_simu(bb_simu_unconc9_s3,nsave=nsave,nrep = nrep)
bb_simu_unconc9_s4=tranform_list_simu(bb_simu_unconc9_s4,nsave=nsave,nrep = nrep)
bb_simu_unconc9_s5=tranform_list_simu(bb_simu_unconc9_s5,nsave=nsave,nrep = nrep)
```

We can then calculate the posterior medians, the 95% credible intervals, the width of the 95% credible intervals, and the coverage of the 95% credible intervals of UNL estimates in each scenario.
```{r}
for(case_i in 1:9){
  median_name=paste("median_uncon","c",case_i,sep="")
  simu_name1=paste("simu_uncon","c",case_i,"_s1",sep="")
  simu_name2=paste("simu_uncon","c",case_i,"_s2",sep="")
  simu_name3=paste("simu_uncon","c",case_i,"_s3",sep="")
  simu_name4=paste("simu_uncon","c",case_i,"_s4",sep="")
  simu_name5=paste("simu_uncon","c",case_i,"_s5",sep="")
  assign(median_name,data.frame(UNL=c(apply(get(simu_name1),FUN=median,MARGIN = 2),
                                      apply(get(simu_name2),FUN=median,MARGIN = 2),
                                      apply(get(simu_name3),FUN=median,MARGIN = 2),
                                      apply(get(simu_name4),FUN=median,MARGIN = 2),
                                      apply(get(simu_name5),FUN=median,MARGIN = 2)),
                                size=as.factor(c(rep("s1",nrep),rep("s2",nrep),rep("s3",nrep),
                                                 rep("s4",nrep),rep("s5",nrep)))))
  
}


for(case_i in 1:9){
  median_name=paste("bb_median_uncon","c",case_i,sep="")
  simu_name1=paste("bb_simu_uncon","c",case_i,"_s1",sep="")
  simu_name2=paste("bb_simu_uncon","c",case_i,"_s2",sep="")
  simu_name3=paste("bb_simu_uncon","c",case_i,"_s3",sep="")
  simu_name4=paste("bb_simu_uncon","c",case_i,"_s4",sep="")
  simu_name5=paste("bb_simu_uncon","c",case_i,"_s5",sep="")
  assign(median_name,data.frame(UNL=c(apply(get(simu_name1),FUN=median,MARGIN = 2),
                                      apply(get(simu_name2),FUN=median,MARGIN = 2),
                                      apply(get(simu_name3),FUN=median,MARGIN = 2),
                                      apply(get(simu_name4),FUN=median,MARGIN = 2),
                                      apply(get(simu_name5),FUN=median,MARGIN = 2)),
                                size=as.factor(c(rep("s1",nrep),rep("s2",nrep),rep("s3",nrep),
                                                 rep("s4",nrep),rep("s5",nrep)))))
  
}


for(case_i in 1:9){
  width_name=paste("width_uncon","c",case_i,sep="")
  simu_name1=paste("simu_uncon","c",case_i,"_s1",sep="")
  simu_name2=paste("simu_uncon","c",case_i,"_s2",sep="")
  simu_name3=paste("simu_uncon","c",case_i,"_s3",sep="")
  simu_name4=paste("simu_uncon","c",case_i,"_s4",sep="")
  simu_name5=paste("simu_uncon","c",case_i,"_s5",sep="")
  assign(width_name,data.frame(width=c(apply(get(simu_name1),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name1),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name2),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name2),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name3),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name3),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name4),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name4),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name5),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name5),FUN=quantile,MARGIN = 2,probs=0.025)),
                               size=as.factor(c(rep("s1",nrep),rep("s2",nrep),rep("s3",nrep),
                                                rep("s4",nrep),rep("s5",nrep)))))
  
}


for(case_i in 1:9){
  width_name=paste("bb_width_uncon","c",case_i,sep="")
  simu_name1=paste("bb_simu_uncon","c",case_i,"_s1",sep="")
  simu_name2=paste("bb_simu_uncon","c",case_i,"_s2",sep="")
  simu_name3=paste("bb_simu_uncon","c",case_i,"_s3",sep="")
  simu_name4=paste("bb_simu_uncon","c",case_i,"_s4",sep="")
  simu_name5=paste("bb_simu_uncon","c",case_i,"_s5",sep="")
  assign(width_name,data.frame(width=c(apply(get(simu_name1),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name1),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name2),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name2),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name3),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name3),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name4),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name4),FUN=quantile,MARGIN = 2,probs=0.025),
                                       apply(get(simu_name5),FUN=quantile,MARGIN = 2,probs=0.975)-
                                         apply(get(simu_name5),FUN=quantile,MARGIN = 2,probs=0.025)),
                               size=as.factor(c(rep("s1",nrep),rep("s2",nrep),rep("s3",nrep),
                                                rep("s4",nrep),rep("s5",nrep)))))
  
}

for(case_i in 1:9){
  for(size_i in 1:5){
    CI_name=paste("CI95_uncon","c",case_i,"_s",size_i,sep="")
    simu_name=paste("simu_uncon","c",case_i,"_s",size_i,sep="")
    assign(CI_name,data.frame(lower=apply(get(simu_name),FUN=quantile,MARGIN = 2,probs=0.025),
                              higher=apply(get(simu_name),FUN=quantile,MARGIN = 2,probs=0.975)))
    
  }
}

coverage=matrix(0,nrow=9,ncol = 5)
for(case_i in 1:9){
  for(size_i in 1:5){
    CI_name=paste("CI95_uncon","c",case_i,"_s",size_i,sep="")
    coverage[case_i,size_i]=sum(true_unl_uncon(case=case_i)>=get(CI_name)[["lower"]]&
                                  true_unl_uncon(case=case_i)<=get(CI_name)[["higher"]])
  }
}

##bb
for(case_i in 1:9){
  for(size_i in 1:5){
    CI_name=paste("bb_CI95_uncon","c",case_i,"_s",size_i,sep="")
    simu_name=paste("bb_simu_uncon","c",case_i,"_s",size_i,sep="")
    assign(CI_name,data.frame(lower=apply(get(simu_name),FUN=quantile,MARGIN = 2,probs=0.025),
                              higher=apply(get(simu_name),FUN=quantile,MARGIN = 2,probs=0.975)))
    
  }
}

bb_coverage=matrix(0,nrow=9,ncol = 5)
for(case_i in 1:9){
  for(size_i in 1:5){
    CI_name=paste("bb_CI95_uncon","c",case_i,"_s",size_i,sep="")
    bb_coverage[case_i,size_i]=sum(true_unl_uncon(case=case_i)>=get(CI_name)[["lower"]]&
                                  true_unl_uncon(case=case_i)<=get(CI_name)[["higher"]])
  }
}
```

## Posterior median boxplots
We can make boxplots of the posterior median of the coefficient of underlap across 100 simulated datasets
for different parameter configurations and sample sizes as following.
```{r}
theme_set(theme_bw())
df <- bind_rows(
  median_unconc1     %>% mutate(Estimator = "DPM"),
  bb_median_unconc1  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc1=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=1), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario I - UNL = ",2.792,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc2     %>% mutate(Estimator = "DPM"),
  bb_median_unconc2  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc2=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=2), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario I - UNL = ",1.919,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc3     %>% mutate(Estimator = "DPM"),
  bb_median_unconc3  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc3=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=3), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario I - UNL = ",1.139,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc4     %>% mutate(Estimator = "DPM"),
  bb_median_unconc4  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc4=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=4), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario II - UNL = ",2.527,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc5     %>% mutate(Estimator = "DPM"),
  bb_median_unconc5  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc5=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=5), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario II - UNL = ",1.855,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc6     %>% mutate(Estimator = "DPM"),
  bb_median_unconc6  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc6=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=6), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario II - UNL = ",1.191,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc7     %>% mutate(Estimator = "DPM"),
  bb_median_unconc7  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc7=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=7), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario III - UNL = ",2.508,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc8     %>% mutate(Estimator = "DPM"),
  bb_median_unconc8  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc8=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=8), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario III - UNL = ",1.933,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  median_unconc9     %>% mutate(Estimator = "DPM"),
  bb_median_unconc9  %>% mutate(Estimator = "DPM-BB")
)
median_box_unconc9=ggplot(df, aes(x=size, y=UNL,fill = Estimator)) + 
  geom_boxplot()+geom_hline(yintercept = true_unl_uncon(case=9), linetype = "solid", color = "red")+
  ggtitle(paste("Scenario III - UNL = ",1.143,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(1,3,by=0.2),limits = c(1,3))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )
```

```{r, fig.width=27, fig.height=16,dpi=300}
cowplot::plot_grid(median_box_unconc1,median_box_unconc2,median_box_unconc3,
                   median_box_unconc4,median_box_unconc5,median_box_unconc6,
                   median_box_unconc7,median_box_unconc8,median_box_unconc9,ncol = 3)
```

## 95% CI width boxplots
We can make the boxplot of the width of the 95% credible intervals of the coefficient of underlap across 100 simulated datasets for varying parameter configurations and sample sizes as following.
```{r}
##width box plots
df <- bind_rows(
  width_unconc1     %>% mutate(Estimator = "DPM"),
  bb_width_unconc1  %>% mutate(Estimator = "DPM-BB")
)
theme_set(theme_bw())
width_box_unconc1=ggplot() + geom_boxplot(data=df, aes(x=size, y=width,fill = Estimator))+
  ggtitle(paste("Scenario I - UNL = ",2.792,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc2     %>% mutate(Estimator = "DPM"),
  bb_width_unconc2  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc2=ggplot() + geom_boxplot(data=df, aes(x=size, y=width,fill = Estimator))+
  ggtitle(paste("Scenario I - UNL = ",1.919,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc3     %>% mutate(Estimator = "DPM"),
  bb_width_unconc3  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc3=ggplot() + geom_boxplot(data=df, aes(x=size, y=width,fill = Estimator))+
  ggtitle(paste("Scenario I - UNL = ",1.139,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc4     %>% mutate(Estimator = "DPM"),
  bb_width_unconc4  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc4=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario II - UNL = ",2.527,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc5     %>% mutate(Estimator = "DPM"),
  bb_width_unconc5  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc5=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario II - UNL = ",1.855,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc6     %>% mutate(Estimator = "DPM"),
  bb_width_unconc6  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc6=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario II - UNL = ",1.191,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc7     %>% mutate(Estimator = "DPM"),
  bb_width_unconc7  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc7=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario III - UNL = ",2.508,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc8     %>% mutate(Estimator = "DPM"),
  bb_width_unconc8  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc8=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario III - UNL = ",1.933,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )

df <- bind_rows(
  width_unconc9     %>% mutate(Estimator = "DPM"),
  bb_width_unconc9  %>% mutate(Estimator = "DPM-BB")
)
width_box_unconc9=ggplot(df, aes(x=size, y=width,fill = Estimator)) + 
  geom_boxplot()+
  ggtitle(paste("Scenario III - UNL = ",1.143,sep=""))+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks =  seq(0,0.5,by=0.1),limits = c(0,0.5))+
  scale_x_discrete(labels=c("(100,100,100)","(200,200,200)","(500,500,500)","(1000,1000,1000)",
                            "(100,300,500)"))+xlab("Sample Size")+ylab("Interval width")+
  scale_fill_manual(values = c("DPM" = "blue", "DPM-BB" = "pink")) +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 13.5)
  )
```

```{r, fig.width=27, fig.height=16,dpi=300}
cowplot::plot_grid(width_box_unconc1,width_box_unconc2,width_box_unconc3,
                   width_box_unconc4,width_box_unconc5,width_box_unconc6,
                   width_box_unconc7,width_box_unconc8,width_box_unconc9,ncol = 3)
```






